{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-07-18 sftrends_manu.Rnw
load figure for tracy, needs caption

\subsubsection{Clam invasion in Suisun Bay}

@@

@@

# subfig labs
txt <- data.frame(
  x = c(as.numeric(as.Date('1979-10-01')), 2500, 25, 0.25),
  y =  c(10000, 15, 4, 3.3), 
  txt = c('(a)', '(c)', '(b)', '(d)')
)
size <- 6

>>>>

\subsubsection{Effects of wastewater treatment}

\subsubsection{Effects of biological invasions}

@@

<<tracy, fig.height = 5, fig.width = 8, out.width = '\\textwidth', fig.cap = 'test'>>=
data(potw_load)

ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank()
  )
lncol <- RColorBrewer::brewer.pal(9, 'Set1')[2]

toplo1 <- filter(potw_load, loc %in% 'tracy' & var %in% c('tn'))
toplo2 <- filter(potw_load, loc %in% 'tracy' & var %in% c('nh4', 'no3', 'orgn'))

ylab <- expression(paste("Total nitrogen load (kg ", d^-1, ")"))
leglabs <- list(
  expression(NH [4] ^ '+'),
  expression(NO [3] ^ '2-'),
  expression('organic N')
  )

p1 <- ggplot(toplo1, aes(x = date, y = val)) + 
  geom_line(colour = lncol) + 
  scale_x_date(expand = c(0, 0)) + 
  scale_y_continuous(ylab, expand = c(0, 0), limits = c(50, 850)) + 
  ptheme

p2 <- ggplot(toplo2, aes(x = date, y = val, group = var, fill = var)) + 
  geom_area(stat = 'identity', position = 'fill') + 
  scale_x_date(expand = c(0, 0)) + 
  scale_fill_brewer(palette = 'Blues', labels = leglabs) + 
  scale_y_continuous('% of total nitrogen', expand = c(0, 0)) + 
  ptheme + 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
    )

grid.arrange(pA, pB, ncol = 1, heights = c(0.8, 1))
@

@@

# subfig labs
txt <- data.frame(
  x = c(as.numeric(as.Date('1979-10-01')), 2500, 25, 0.25),
  y =  c(10000, 14, 4, 3.3), 
  txt = c('(a)', '(c)', '(b)', '(d)')
)
size <- 6
